---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
library(fagin)
```

Fagin is a program for analyzing orphan genes. The first step of the analysis
is gathering the required data. Inputs are organized into a `config` object,
below are the default values:

```{r}
config()
```

There are many parameters that may be set, but the only ones we need to think
about for now are those under the input header. The command `config()` creates
a default config as an R S4 class. The values may be modified:

```{r}
myConfig <- config()
myConfig@input@gff_dir = "foo/gff"
```

Once the config is loaded with paths to the input data, you can load the data
into the Fagin analysis.

```{r, eval=FALSE}
dat <- load_data(myConfig)
```

This function parses and stores all the raw data required for the analysis and
will (hopefully) pick up any erros before they become problems later.
